---
title: "HW5"
author: "John Weng"
date: "October 15, 2015"
output: 
  html_document:
    keep_md: true
---

```{r}
# https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv
Country.GDP <- read.csv("https://raw.githubusercontent.com/jcweng/stat6306introdatascience/master/Country%20GDP.csv")
Country <- read.csv(url("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv "))

MergeData1 <- merge(x = Country.GDP, y=Country, by = "CountryCode", all.x=TRUE)
nrow(MergeData1)
```

The data set include all Country.GDP observations, and there are a total of 190 observations.
```{r}
View(MergeData1 ) 
nrow(Country)-nrow(Country.GDP)
```
There are observations 44 excluded

**Question 2** 
```{r}
MergeData1 <-MergeData1[order(-MergeData1$Ranking),]
```

ascending order by GDP rank (so United States is last)
```{r}
tail(MergeData1[seq(1,5)], n=5)
```

**Question 3** 
```{r}
attach(MergeData1)
m1 <- MergeData1[ which(MergeData1$Income.Group=="High income: OECD"),]
m2 <- MergeData1[ which(MergeData1$Income.Group=="High income: nonOECD"),]

m1<-m1[order(m1$Ranking),] 
m2<-m2[order(m2$Ranking),] 
round(mean(m1$Ranking))
nrow(m1)
nrow(m2)
```

there is a total of 30 "High income: OECD", with mean GDP rank of 33:
```{r}
round(mean(m1$Ranking))
```
there is a total of 23 "High income: nonOECD", with mean GDP rank of 92:
```{r}
round(mean(m2$Ranking))
```

**Question 4** 
```{r}
MergeData1$GDP.G <-cut(MergeData1$Ranking,c(-Inf,seq(38,152,by=38),Inf), labels = seq(1,5))
attach(MergeData1)

mytable <- table(GDP.G,Income.Group) # A will be rows, B will be columns 
mytable # print table 
```

there are 5 countries that are Lower middle income but among the 38 nations with highest GDP.

**Question 5** 
```{r}
summary(Lending.category)
a <-MergeData1[complete.cases(MergeData1),]

nrow(a)
```
If only complete cases are considered on every single catagory, only 14 makes the cut. I assume we are considering those with GDP rank and there are 190 observations. Certainly, if certain variables are allow to have missing value, NA, than we will have more observations.
