---
title: "Homework 6"
author: "John Weng"
date: "November 18, 2015"
output: 
  html_document:
    keep_md: true
---

Explore the dependence of the probability that a person has positive self-esteem on log annual income (Income2005), intelligence (AFQT), years of education (educ), and gender (data= ex1223.csv).

**Organizing Data**
In first step, I need to do some data manipulations. I created E1 as to group those with Esteem1 = 1 and Esteem1 that are not equal 1. Next. I added l.Income2005 as the logged Income2005. 

```{r}
library("Sleuth3")
set.seed(1234)

E1 <- 0
E1[ex1223$Esteem1 != 1] = 0 
E1[ex1223$Esteem1 == 1] = 1
ex1223$E1 <- E1

l.Income2005 <- log(ex1223$Income2005)
ex1223$l.Income2005 <- l.Income2005 
```

Here I created the the Training and the Test data set. They are ex1223.train and  ex1223.test.
```{r}
dev <- sample(2, nrow(ex1223), replace=TRUE, prob=c(0.67, 0.33))
ex1223.train <- ex1223[dev==1,]
ex1223.test <- ex1223[dev==2,]
```
**Determine the Model**
The first model.1, I have Income2005, AFQT, Educ, Gender as my predictors. Here Income2005 is not logged. By backward elimination, I have reduce to to just AFQT and Educ. The third model, model.3, does seem to best model by AIC. 
```{r, }
model.1 <- glm( E1 ~ Income2005+AFQT+Educ+Gender, data = ex1223.train, family="binomial")
summary(model.1) # AIC: 2344.9

model.2 <- update(model.1, ~ . - Gender) # remove model
summary(model.2) # AIC: 2343

model.3 <- update(model.2, ~ . - Income2005 ) # remove income
summary(model.3) # AIC: 2341.6
```
model.4, I have l.Income2005, AFQT, Educ, Gender as my predictors. Here l.Income2005 is logged. By backward elimination, I have reduce to to just AFQT and Educ. model.5, does seem to best model by AIC, even though Gender appears to be statisticsally insignficent (p-value: 0.010045)
```{r, }
model.4 <- glm( E1 ~ l.Income2005+AFQT+Educ+Gender, data = ex1223.train, family="binomial")
summary(model.4) # AIC: 2341.5

model.5 <- update(model.4, ~ . - Gender) # remove Gender
summary(model.5) # AIC: 2339.8

model.6 <- update(model.5, ~ . - l.Income2005 ) # remove income
summary(model.6) # AIC: 2341.6

```
*Are both variables needed to obtain the best classification?*
No not all variables are need to obtain the best classification.
*Which classifier is better?*
l.Income2005, AFQT, and Educ

**confusion table**
Fitting the model.5 in the test data set. To Obtain  "confusion table" for my classifier. 
```{r, }
pred <- predict(model.5, newdata=ex1223.test,type = "response")
pred <- round(pred)
t = table(Esteem = ex1223.test$E1,Esteem.Pred = pred)
catnames = levels(ex1223.train$E1)
rownames(t) <- c("Positive","Not Positive")
colnames(t) <- c("Positive","Not Positive")
t
```